%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Andrea}{Rau}

\position{Research Director • Directrice de Recherche}
\address{INRAE • French National Research Institute for Agriculture,
Food and Environment}

\mobile{+33 1 34 65 22 82}
\email{\href{mailto:andrea.rau@inrae.fr}{\nolinkurl{andrea.rau@inrae.fr}}}
\homepage{andrea-rau.com}
\orcid{0000-0001-6469-488X}
\googlescholar{9\_\_bzfgAAAAJ}
\github{andreamrau}
\twitter{andreamrau}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {January 2023}
    {Andrea Rau~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{about-me}{%
\section{About me}\label{about-me}}

My research is focused on developing and writing software for sound
statistical methods for genomic and transcriptomic data analysis,
including differential expression analyses, co-expression analyses,
network inference, and integrative multi-omic analyses.

I am a member of the
\href{https://www6.jouy.inra.fr/gabi_eng/}{\textbf{Animal Genetics and
Integrative Biology}} (GABI) research unit (Jouy en Josas, France) in
the Genomics, Biodiversity, Bioinformatics, Statistics (GiBBS) team.

\emph{Keywords}: Analysis of high-throughput sequencing data, mixture
models, supervised classification methods, multi-omic integration, gene
regulatory networks

\emph{Languages}: English (maternal), French (fluent)

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Université d’Évry-Val-d’Essonne}{HDR in Applied Mathematics}{2017}{Évry, France}{\begin{cvitems}
\item Title: Statistical methods and software for the analysis of transcriptomic data \\ Note: An HDR is the French accreditation to supervise research and represents the highest French academic qualification level based on independent scholarship. It is reviewed by and defended before an academic committee.
\end{cvitems}}
    \cventry{Purdue University}{PhD in Statistics}{2007-2010}{West Lafayette, Indiana, USA}{\begin{cvitems}
\item Title: Reverse engineering gene regulatory networks using genomic time-course data \\ Advisors: Rebecca W. Doerge, Jean-Louis Foulley, and Florence Jaffrézic
\end{cvitems}}
    \cventry{Purdue University}{MS in Applied Statistics}{2005-2007}{West Lafayette, Indiana, USA}{\begin{cvitems}
\item Internship: Time series modeling of advertising interventions on pharmacy sales (Walgreens; Deerfield, Illinois, USA)
\end{cvitems}}
    \cventry{Saint Olaf College}{BA in French and Mathematics (concentration in Statistics)}{2001-2005}{Northfield, Minnesota, USA}{\begin{cvitems}
\item Internship: pharmacokinetic analysis of Phase I clinical trial data using a limited-sample model (Mayo Clinic; Rochester, Minnesota, USA)
\end{cvitems}}
\end{cventries}

\hypertarget{work-experience}{%
\section{Work experience}\label{work-experience}}

\begin{cventries}
    \cventry{INRAE}{Research Director (Directrice de Recherche)}{2023-present}{Jouy-en-Josas, France}{}\vspace{-4.0mm}
    \cventry{INRAE}{Research Scientist (Chargée de Recherche)}{2011-2022}{Jouy-en-Josas, France}{}\vspace{-4.0mm}
    \cventry{Medical College of Wisconsin (4 months)}{Adjunct Assistant Professor}{2019}{Milwaukee, Wisconsin, USA}{}\vspace{-4.0mm}
    \cventry{Zilber School of Public Health, University of Wisconsin-Milwaukee (20 months)}{AgreenSkills+ Visiting Scholar}{2017-2019}{Milwaukee, Wisconsin, USA}{}\vspace{-4.0mm}
    \cventry{Zilber School of Public Health, University of Wisconsin-Milwaukee  (6 weeks)}{Visiting Scholar}{2016}{Milwaukee, Wisconsin, USA}{}\vspace{-4.0mm}
    \cventry{Ensai}{Adjunct Assistant Professor}{2012-2017}{Rennes, France}{}\vspace{-4.0mm}
    \cventry{Inria - Île-de-France}{Post-doctoral researcher}{2010-2011}{Orsay, France}{}\vspace{-4.0mm}
    \cventry{Department of Statistics, Purdue University (R. W. Doerge}{Research assistant}{2008-2010}{West Lafayette, Indiana, USA}{}\vspace{-4.0mm}
    \cventry{Department of Statistics, Purdue University}{Consultant in the Statistical Consulting Service}{2007}{West Lafayette, Indiana, USA}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{awards}{%
\section{Awards}\label{awards}}

\begin{cvhonors}
    \cvhonor{}{Graduate Women in Science Programs travel award}{2010}{\rightarrow}
    \cvhonor{}{Student travel award, Conference on Applied Statistics in Agriculture at Kansas State University}{2010}{\rightarrow}
    \cvhonor{}{Honorable mention, Gertrude M. Cox Scholarship}{2009}{\rightarrow}
    \cvhonor{}{A.H. Ismail Interdisciplinary Program doctoral research travel award}{2009}{\rightarrow}
\end{cvhonors}

\hypertarget{professional-organizations}{%
\section{Professional organizations}\label{professional-organizations}}

\begin{cvhonors}
    \cvhonor{}{Femmes \& Sciences}{2022-present}{F\&S}
    \cvhonor{}{Société Française de la Statistique}{2011-present}{SFdS}
    \cvhonor{}{American Statistical Association}{2005-present}{ASA}
\end{cvhonors}

\hypertarget{dissertations-books-book-chapters}{%
\section{Dissertations, books \& book
chapters}\label{dissertations-books-book-chapters}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Duranthon, V., Araújo, S., Palma, M., \textbf{Rau, A.}, Matzapetakis,
  M., and Almeida, A. (2021) Rabbit research in the post-genomic era:
  transcriptome, proteome, and metabolome analysis. \emph{In: The
  Genetics and Genomics of the Rabbit}, Ed. L. Fontanesi.
\item
  \textbf{Rau, A.} (2017) Statistical methods and software for the
  analysis of transcriptomic data. \emph{HDR thesis}, Université d'Évry
  Val-d'Essonne.
\item
  Martin-Magniette, M.-L., Maugis-Rabusseau, C. and \textbf{Rau, A.}
  (2017) Clustering of co-expressed genes. \emph{In: Model Choice and
  Model Aggregation}, Ed. F. Bertrand, J.-J. Droesbeke, G. Saporta, C.
  Thomas-Agnan.
\item
  Albert, I., Ancelet, S., David, O., Denis, J.-B., Makowski, D.,
  Parent, É., \textbf{Rau, A.}, and Soubeyrand, S. (2015) Initiation à
  la statistique bayésienne : Bases théoriques et applications en
  alimentation, environnement, épidémiologie et génétique.
  \emph{Éditions Ellipses}, collection références sciences.
\item
  \textbf{Rau, A.} (2010) Reverse engineering gene networks using
  genomic time-course data.. \emph{PhD thesis}, Purdue University.
\end{enumerate}

\hypertarget{peer-reviewed-publications}{%
\section{Peer-reviewed publications}\label{peer-reviewed-publications}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Mollandin, F., Gilbert, H., Croiseau, P., and \textbf{Rau, A.} (2022)
  Accounting for overlapping annotations in genomic prediction models of
  complex traits. \emph{BMC Bioinformatics}, 23:65.
  \url{https://dx.doi.org/10.1186/s12859-022-04914-5}
\item
  Mazurier, M., Drouaud, J., Bahrman, N., \textbf{Rau, A.},
  Lejeune-Hénaut, I., Delbreil, B., and Legrand, S. (2022) Integrated
  sRNA-seq and RNA-seq analyses reveal a microRNA regulation network
  involved in cold response in Pisum sativum L. \emph{Genes}, 13:1119.
  \url{https://dx.doi.org/10.3390/genes13071119}
\item
  \textbf{Rau, A.}, Passet, B., Castille, J., Asset, A., Lecardonnel,
  J., Moroldo, M., Jaffrézic, F., Laloë, D., Moazami-Goudarzi, K., and
  Vilotte, J.-L. (2022) Potential genetic robustness of Prnp and Sprn
  double knockout mouse embryos towards ShRNA-lentiviral inoculation.
  \emph{Veterinary Research}, 53:54.
  \url{https://dx.doi.org/10.1186/s13567-022-01075-4}
\item
  Cazals, A., \textbf{Rau, A.}, Estellé, J., Bruneau, N., Coville,
  J.-L., Menanteau, P., Rossignol, M.-N., Jardet, D., Bevilacqua, C.,
  Bed'Hom, B., Velge, P., and Calenge, F. (2022) Comparative analysis of
  the caecal tonsil transcriptome in two chicken lines experimentally
  infected with Salmonella Enteritidis. \emph{PLoS ONE}, 17(8):
  e0270012. \url{https://dx.doi.org/10.1371/journal.pone.0270012}
\item
  Cazals, A., Estellé, J., Bruneau, N., Coville, J.-L., Menanteau, P.,
  Rossignol, M.-N., Jardet, D., Bevilacqua, C., \textbf{Rau, A.},
  Bed'Hom, B., Velge, P., and Calenge, F. (2022) Differences in caecal
  microbiota composition and Salmonella carriage between experimentally
  infected inbred lines of chickens. \emph{Genetics Selection
  Evolution}, 54:7. \url{https://dx.doi.org/10.1186/s12711-022-00699-6}
\item
  \textbf{Rau, A.}, Manansala, R., Flister, M. J., Rui, H., Jaffrézic,
  F., Laloë, D., and Auer, P. L. (2022) Individualized multi-omic
  pathway deviation scores using multiple factor analysis.
  \emph{Biostatistics}, 23(2):362-379.
  \url{https://dx.doi.org/10.1093/biostatistics/kxaa029}
\item
  \textbf{Rau, A.} (2021) Cooking up knowledge from big data using data
  science. \emph{Frontiers in Young Minds}, 9:632923.
  \url{https://dx.doi.org/10.3389/frym.2021.632923}
\item
  Mollandin, F., \textbf{Rau, A.}, and Croiseau, P. (2021) An evaluation
  of the predictive performance and mapping power of the BayesR model
  for genomic prediction. \emph{G3}, jkab225.
  \url{https://dx.doi.org/10.1093/g3journal/jkab225}
\item
  Sellem, E., Marthey, S., \textbf{Rau, A.}, Jouneau, L., Bonnet, A., Le
  Danvic, C., Kiefer, H., Jammes, H., and Schibler, L. (2021) Dynamics
  of cattle sperm sncRNAs during maturation, from testis to ejaculated
  sperm. \emph{Epigenetics and Chromatin}, 14:24.
  \url{https://dx.doi.org/10.1186/s13072-021-00397-5}
\item
  Mach, N., Moroldo, M., \textbf{Rau, A.}, Lecardonnel, J., Le Moyec,
  L., Robert, C., and Barrey, E. (2021) Understanding the holobiont:
  crosstalk between gut microbiota and mitochondria during endurance.
  \emph{Frontiers Molecular Biosciences}, 8:656204.
  \url{https://dx.doi.org/10.3389/fmolb.2021.656204}
\item
  Devogel, N., Auer, P. L., Manansala, R., \textbf{Rau, A.}, and Wang,
  T. (2021) A unified linear mixed model for familial relatedness and
  population structure in genetic association studies. \emph{Genetic
  Epidemiology}, 45(3): 305-315.
  \url{https://dx.doi.org/10.1002/gepi.22371}
\item
  Cho, Y., \textbf{Rau, A.}, Reiner, A., Auer, P. L. (2020) Mendelian
  randomization analysis with survival outcomes. \emph{Genetic
  Epidemiology}, 45(1): 16-23.
  \url{https://dx.doi.org/10.1002/gepi.22354}
\item
  Sellem, E., Marthey, S., \textbf{Rau, A.}, Jouneau, L., Bonnet, A.,
  Perrier, J.-P., Fritz, S., Le Danvic, C. Boussaha, M., Kiefer, H.,
  Jammes, H., Schiblier, L. (2020) A comprehensive overview of bull
  sperm-borne small non-coding RNAs and their diversity in six breeds.
  \emph{Epigenetics and Chromatin}, 13:19.
  \url{https://dx.doi.org/10.1186/s13072-020-00340-0}
\item
  Godichon-Baggioni, A., Maugis-Rabusseau, C. and \textbf{Rau, A.}
  (2020) Multi-view cluster aggregation and splitting, with an
  application to multi-omic breast cancer data. \emph{Annals of Applied
  Statistics}, 14:2, 752-767.
  \url{https://dx.doi.org/10.1214/19-AOAS1317}
\item
  Jehl, F., Désert, C., Klopp, C., Brenet, M., \textbf{Rau, A.}, Leroux,
  S., Boutin, M., Muret, K., Blum, Y., Esquerré, D., Gourichon, D.,
  Burlot, T., Collin, A., Pitel, F., Benani, A., Zerjal, T., Lagarrigue,
  S. (2019) Chicken adaptive response to low energy diet: main role of
  the hypothalamic lipid metabolism revealed by a phenotypic and
  multi-tissue transcriptomic approach. \emph{BMC Genomics}, 20.
  \url{https://dx.doi.org/10.1186/s12864-019-6384-8}
\item
  Foissac, S., Djebali, S., Munyard, K., Villa-Vialaneix, N.,
  \textbf{Rau, A.}, Muret, K., Esquerre, D., Zytnicki, M., Derrien, T.,
  Bardou, P., Blanc, F., Cabau, C., Crisci, E., Dhorne-Pollet, S.,
  Drouet, F., Gonzales, I., Goubil, A., Lacroix-Lamande, S., Laurent,
  F., Marthey, S., Marti-Marimon, M., Momal-Leisenring, R., Mompart, F.,
  Quere, P., Robelin, D., San Cristobal, M., Tosser-Klopp, G.,
  Vincent-Naulleau, S., Fabre, S., Pinard-Van der Laan, M.-H., Klopp,
  C., Tixier-Boichard, M., Acloque, H., Lagarrigue, S., Giuffra, E.
  (2019) Multi-species annotation of transcriptome and chromatin
  structure in domesticated animals. \emph{BMC Biology}, 18:48.
  \url{https://dx.doi.org/10.1186/s12915-019-0726-5}
\item
  Dhara, S., \textbf{Rau, A.}, Flister, M., Recka, N., Laiosa, M., Auer,
  P., and Udvadia, A. (2019) Cellular reprogramming for successful CNS
  axon regeneration is driven by a temporally changing cast of
  transcription factors. \emph{Scientific Reports}, 9:14198.
  \url{https://dx.doi.org/10.1038/s41598-019-50485-6}
\item
  \textbf{Rau, A.}, Dhara, S., Udvadia, A., and Auer, P. (2019)
  Regeneration Rosetta: An interactive web application to explore
  regeneration-associated gene expression and chromatin accessibility.
  \emph{G3: Genes\textbar Genomes\textbar Genetics}, 9(12): 3953-3959.
  \url{https://dx.doi.org/10.1534/g3.119.400729}
\item
  Plasterer, C., Tsaih, S.-W., Lemke, A., Schilling, R., Dwinell, M.,
  \textbf{Rau, A.}, Auer, P., Rui, H., Flister, M.J. (2019)
  Identification of a rat mammary tumor risk locus that is syntenic with
  the commonly amplified 8q12.1 and 8q22.1 regions in human breast
  cancer patients. \emph{G3: Genes\textbar Genomes\textbar Genetics},
  9(5): 1739-1743. \url{https://dx.doi.org/10.1534/g3.118.200873}
\item
  Ramayo-Caldas, Y., Zingaretti, L., Bernard, A., Estellé, J. Popova,
  M., Pons, N., Bellot, P., Mach, N., \textbf{Rau, A.}, Roume, H.,
  Perez-Encisco, M., Faverdin, P., Edouard, N., Dusko, S., Morgavi, D.P.
  and Renand, G. (2019) Identification of rumen microbial biomarkers
  linked to methane emission in Holstein dairy cows. \emph{Journal of
  Animal Breeding and Genetics}, 137:49-59.
  \url{https://dx.doi.org/10.1111/jbg.12427}
\item
  \textbf{Rau, A.}, Flister, M. J., Rui, H. and Livermore Auer, P.
  (2019) Exploring drivers of gene expression in The Cancer Genome
  Atlas. \emph{Bioinformatics}, 35(1): 62-68.
  \url{https://dx.doi.org/10.1093/bioinformatics/bty551}
\item
  Godichon-Baggioni, A., Maugis-Rabusseau, C. and \textbf{Rau, A.}
  (2018) Clustering transformed compositional data using K-means, with
  applications in gene expression and bicycle sharing system data.
  \emph{Journal of Applied Statistics}, 46(1):47-65.
  \url{https://dx.doi.org/10.1080/02664763.2018.1454894}
\item
  \textbf{Rau, A.} and Maugis-Rabusseau, C. (2018) Transformation and
  model choice for RNA-seq co-expression analysis. \emph{Briefings in
  Bioinformatics}, bbw128. \url{https://dx.doi.org/10.1093/bib/bbw128}
\item
  Verrier, E., Genet, C., Laloë, D., Jaffrézic, J., \textbf{Rau, A.},
  Esquerre, D., Dechamp, N., Ciobataru, C., Hervet, C., Krieg, F.,
  Quillet, E., Boudinot, P. (2018) Genetic and transcriptomic analyses
  provide new insights on the early antiviral response to VHSV in
  resistant and susceptible rainbow trout. \emph{BMC Genomics}, 19:482.
  \url{https://dx.doi.org/10.1186/s12864-018-4860-1}
\item
  Maroilley, T., Berri, M., Lemonnier, G., Esquerré, D., Chevaleyre, C.,
  Mélo, S., Meurens, F., Coville, J.L., Leplat, J.J, \textbf{Rau, A.},
  Bed'hom, B., Vincent-Naulleau, S., Mercat, M.J., Billon, Y., Lepage,
  P., Rogel-Gaillard, C., and Estellé, J. (2018) Immunome differences
  between porcine ileal and jejunal Peyer's patches revealed by global
  transcriptome sequencing of gut-associated lymphoid tissues.
  \emph{Scientific Reports}, 8:9077.
  \url{https://dx.doi.org/10.1038/s41598-018-27019-7}
\item
  Mondet, F., \textbf{Rau, A.}, Klopp, C., Rohmer, M. Severac, D., Le
  Conte, Y., and Alaux, C. (2018) Transcriptome profiling of the
  honeybee parasite Varroa destructor provides new biological insights
  into the mite adult life cycle. \emph{BMC Genomics}, 19:328.
  \url{https://dx.doi.org/10.1186/s12864-018-4668-z}
\item
  He, B., Tjhung, K., Bennett, N., Chou, Y., \textbf{Rau, A.}, Huang,
  J., and Derda, R. (2018) Compositional bias in naïve and
  chemically-modified phage-displayed libraries uncovered by paired-end
  deep sequencing. \emph{Scientific Reports}, 8:1214.
  \url{https://dx.doi.org/10.1038/s41598-018-19439-2}
\item
  Monneret, G., Jaffrézic, F., \textbf{Rau, A.}, Zerjal, T. and Nuel, G.
  (2017) Identification of marginal causal relationships in gene
  networks from observational and interventional expression data.
  \emph{PLoS One}, 12(3): e0171142.
  \url{https://dx.doi.org/10.1371/journal.pone.0171142}
\item
  Sauvage, C., \textbf{Rau, A.}, Aichholz, C., Chadoeuf, J., Sarah, G.,
  Ruiz, M., Santoni, S., Causse, M., David, J., Glémin, S. (2017)
  Domestication rewired gene expression and nucleotide diversity
  patterns in tomato. \emph{The Plant Journal}, 91(4):631-645.
  \url{https://dx.doi.org/10.1111/tpj.13592}
\item
  Rigaill, G., Balzergue, S., Brunaud, V., Blondet, E., \textbf{Rau,
  A.}, Rogier, O., Caius, J., Maugis-Rabusseau, C., Soubigou-Taconnat,
  L., Aubourg, S., Lurin, C., Martin-Magniette, M.-L., and Delannoy, E.
  (2016) Synthetic datasets for the identification of key ingredients
  for RNA-seq differential analysis. \emph{Briefings in Bioinformatics},
  19(1):65-76. \url{https://dx.doi.org/10.1093/bib/bbw092}
\item
  Gallopin, M., Celeux, G., Jaffrézic, F., \textbf{Rau, A.} (2015) A
  model selection criterion for model-based clustering of annotated gene
  expression data. \emph{Statistical Applications in Genetics and
  Molecular Biology}, 14(5): 413-428.
  \url{https://dx.doi.org/10.1515/sagmb-2014-0095}
\item
  Monneret, G., Jaffrézic, F., \textbf{Rau, A.}, Nuel, G. (2015)
  Estimation d'effets causaux dans les réseaux de régulation génique :
  vers la grande dimension. \emph{Revue d'intelligence artificielle},
  29(2): 205-227.
\item
  \textbf{Rau, A.}, Maugis-Rabusseau, C., Martin-Magniette, M.-L.,
  Celeux, G. (2015) Co-expression analysis of high-throughput
  transcriptome sequencing data with Poisson mixture models.
  \emph{Bioinformatics}, 31(9): 1420-1427.
  \url{https://dx.doi.org/10.1093/bioinformatics/btu845}
\item
  \textbf{Rau, A.}, Marot, G. and Jaffrézic, F. (2014) Differential
  meta-analysis of RNA-seq data from multiple studies. \emph{BMC
  Bioinformatics}, 16:31.
  \url{https://dx.doi.org/10.1186/1471-2105-15-91}
\item
  Endale Ahanda, M.-L., Zerjal, T., Dhorne-Pollet, S., \textbf{Rau, A.},
  Cooksey, A., and Giuffra, E. (2014) Impact of the genetic background
  on the composition of the chicken plasma miRNome in response to a
  stress. \emph{PLoS One}, 9(12): e114598.
  \url{https://dx.doi.org/10.1371/journal.pone.0114598}
\item
  Nuel, G., \textbf{Rau, A.}, and Jaffrézic, F. (2013) Using pairwise
  ordering preferences to estimate causal effects in gene expression
  from a mixture of observational and intervention experiments..
  \emph{Quality Technology and Quantitative Management}, 11(1):23-37.
  \url{https://dx.doi.org/10.1080/16843703.2014.11673323}
\item
  \textbf{Rau, A.}, Jaffrézic, F., and Nuel, G. (2013) Joint estimation
  of causal effects from observational and intervention gene expression
  data. \emph{BMC Systems Biology}, 8:51.
  \url{https://dx.doi.org/10.1186/1752-0509-7-111}
\item
  Gallopin, M. \textbf{Rau, A.}, and Jaffrézic, F. (2013) A hierarchical
  Poisson log-normal model for network inference from RNA sequencing
  data. \emph{PLoS One}, 8(10): e77503.
  \url{https://dx.doi.org/10.1371/journal.pone.0077503}
\item
  \textbf{Rau, A.}, Gallopin, M., Celeux, G., and Jaffrézic, F. (2013)
  Data-based filtering for replicated high-throughput transcriptome
  sequencing experiments. \emph{Bioinformatics}, 29(17): 2146-2152.
  \url{https://dx.doi.org/10.1093/bioinformatics/btt350}
\item
  Dillies, M.-A., \textbf{Rau, A.}, Aubert, J., Hennequet-Antier, C.,
  Jeanmougin, M., Servant, N., Keime, C., Marot, G., Castel, D.,
  Estelle, J., Guernec, G., Jagla, B., Jouneau, L., Laloë, D., Le Gall,
  C., Schaëffer, B., Charif, D., Le Crom, S., Guedj, M., and Jaffrézic,
  F. (2013) A comprehensive evaluation of normalization methods for
  Illumina high-throughput RNA sequencing data analysis. \emph{Briefings
  in Bioinformatics}, 14(6): 671-683.
  \url{https://dx.doi.org/10.1093/bib/bbs046}
\item
  Brenault, P., Lefevre, L. \textbf{Rau, A.}, Laloë, D., Pisoni, G.,
  Moroni, P., Bevilacquia, C. and Martin, P. (2013) Contribution of
  mammary epithelial cells to the immune response during early stages of
  a bacterial infection to Staphylococcus aureus. \emph{Veterinary
  Research}, 45:16. \url{https://dx.doi.org/10.1186/1297-9716-45-16}
\item
  \textbf{Rau, A.}, Jaffrézic, F., Foulley, J.-L., and Doerge, R. W.
  (2012) Reverse engineering gene regulatory networks using approximate
  Bayesian computation. \emph{Statistics and Computing}, 22: 1257-1271.
  \url{https://dx.doi.org/10.1007/s11222-011-9309-1}
\item
  \textbf{Rau, A.}, Jaffrézic, F., Foulley, J.-L., and Doerge, R. W.
  (2010) An empirical Bayesian method for estimating biological networks
  from temporal microarray data. \emph{Statistical Applications in
  Genetics and Molecular Biology}, 9(1): 9.
  \url{https://dx.doi.org/10.2202/1544-6115.1513}
\item
  Furth, A., Mandrekar, S., Tan, A. \textbf{Rau, A.}, Felten, S., Ames,
  M. Adjei, A. Erlichman, C. and Reid, J. (2008) A limited sample model
  to predict area under the drug concentration curve for
  17-(allylamino)-17-demethoxygeldanamycin and its active metabolite
  17-(amino)-17-demethoxygeldanomycin. \emph{Cancer Chemotherapy
  Pharmacology}, 61(1): 39-45.
  \url{https://dx.doi.org/10.1007/s00280-007-0443-6}
\end{enumerate}

\hypertarget{pre-prints-technical-reports-other-publications}{%
\section{Pre-prints, technical reports, \& other
publications}\label{pre-prints-technical-reports-other-publications}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Duran Garzon, C., Chemin, C., \textbf{Rau, A.}, Decaux, B.,
  Sellier-Richard, H., Drouaud, J., Soubigou-Taconnat, L., Brunaud, V.,
  Martin, M.-L., Palaffre, C., Rayon, C., Lourgant, K., Guénin, S.
  Gutierrez, L., Charcosset, A., Coursol, S., and Giauffret, C. (2022)
  Integrative analysis of genetic and transcriptomic data reveals
  volatile terpenoids biosynthesis genes linked with chilling tolerance.
  Submitted.
\item
  Noël, A., Dumas, C., Rottier, E., Beslay, D., Costagliola, G., Ginies,
  C., Nicolè, F., \textbf{Rau, A.}, Le Conte, Y., and Mondet, F. (2022)
  Volatolome of the honey bee (Apis mellifera) worker brood: from egg to
  emergence. Submitted.
\item
  Mollandin, F., Gilbert, H., Croiseau, P., and \textbf{Rau, A.} (2022)
  Capitalizing on complex annotations in Bayesian genomic prediction for
  a backcross population of growing pigs. \emph{12th World Congress on
  Genetics Applied to Livestock Production (3-8 July 2022)} Rotterdam,
  Netherlands.
\item
  Mazo, G., Karlis, D., and \textbf{Rau, A.} (2022) A randomized
  pairwise likelihood method for complex statistical inferences.
  Submitted. \url{https://hal.archives-ouvertes.fr/hal-03126621}
\item
  Bruford, M., Leroy, G., Orozco-terWengel, P., \textbf{Rau, A.}, and
  Simianer H. (2015) Section B: Molecular tools for exploring genetic
  diversity. \emph{The Second Report on the State of the World's Animal
  Genetic Resources for Food and Agriculture} FAO Commission on Genetic
  Resources for Food and Agriculture.
\item
  Nuel, G., \textbf{Rau, A.}, and Jaffrézic, F. (2013) Joint likelihood
  calculation for intervention and observational data from a Gaussian
  Bayesian network. \emph{arXiv} 1305.0709.
\item
  \textbf{Rau, A.}, Celeux, G., Martin-Magniette, M.-L., and
  Maugis-Rabusseau, C. (2011) Clustering high-throughput sequencing data
  with Poisson mixture models. \emph{Inria Research Report} 7786.
\item
  \textbf{Rau, A.}, Jaffrézic, F., Foulley, J.-L., and Doerge, R. W.
  (2010) Approximate Bayesian approaches for reverse engineering
  biological networks. \emph{Proceedings of the Kansas State University
  Conference on Applied Statistics in Agriculture} Manhattan, Kansas.
\item
  \textbf{Rau, A.} (2008) Success of Volunteer Statistical Consulting
  Service Leads to Expanded Network. \emph{The Statistical Consultant}
  25(1).
\item
  \textbf{Rau, A.} (2008) STATCOM Network Engages Growing Number of
  Student Volunteers. \emph{Newsletter for the Section on Statistical
  Education} 13(1).
\item
  \textbf{Rau, A.} (2008) Success of Statistical Service Leads to
  Expanded Network. \emph{Amstat News} April 2008.
\end{enumerate}

\hypertarget{conference-presentations}{%
\section{Conference presentations}\label{conference-presentations}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{(Invited talk) Leveraging multi-omic data for integrative
  exploratory and predictive analyses}\\
  Journées Math Bio Santé du GDR MATHSAV @ Besançon (2022-10-06)
\item
  \textbf{(Poster) A hierarchical Bayesian mixture model for predicting
  phenotypes from genomic data with prior biological information}\\
  Working Group on Model-Based Clustering Summer Session @ virtual
  (2022-07-26)
\item
  \textbf{(Invited talk) Mixture models as a useful tool for identifying
  co-expressed genes from RNA-seq data}\\
  MiMo Workshop on mixture models @ virtual (2021-04-08)
\item
  \textbf{(Invited keynote) Integrative and interactive analyses of
  multi-omics data}\\
  JOBIM 2020 @ virtual (2020-07-02)
\item
  \textbf{(Invited talk) Individualized multi-omic pathway deviation
  scores using multiple factor analysis}\\
  EuroBioc 2019 @ Brussels, Belgium (2019-12-09)
\item
  \textbf{(Poster) Integrative methods for multi-omic data reveal
  multi-level gene and pathway regulation}\\
  AgreenSkills+ annual meeting @ Brussels, Belgium (2019-04-12)
\item
  \textbf{coseq, An R/Bioconductor package for co-expression analyses of
  RNA-seq data}\\
  Plant and Animal Genomes (PAG) XXVI @ San Diego, California, USA
  (2018-01-15)
\item
  \textbf{(Invited talk) Model-based clustering to identify co-expressed
  genes from high-throughput sequencing data}\\
  Working Group on Model-Based Clustering @ Perugia, Italy (2017-07-20)
\item
  \textbf{Clustering transformed compositional data using coseq}\\
  useR!2017 @ Brussels, Belgium (2017-07-05)
\item
  \textbf{(Invited talk, FAANG workshop) An update on the FAANG pilot
  project FR-AgENCODE}\\
  Plant and Animal Genomes (PAG) XXVI @ San Diego, California, USA
  (2017-01-12)
\item
  \textbf{(Invited talk) Statistical tools to identify and visualize
  co-expression clusers from RNA-seq data}\\
  INRA RNA-seq day @ Avignon (2016-11-17)
\item
  \textbf{Identifying marginal causal relationships in gene networks
  from observational and interventional expression data}\\
  Joint Statistical Meetings of the American Statistical Association @
  Chicago (2016-07-31)
\item
  \textbf{(Invited talk) Experimental design in 'omics studies}\\
  2nd International Symposium on Microgenomics, Technical Workshop @
  Jouy-en-Josas (2016-05-31)
\item
  \textbf{HTSCluster, a mixture-based approach for co-expression
  analyses of RNA-seq data}\\
  15th Workshop: Statistical Methods for Post-Genomic Data @ Munich
  (2015-02-13)
\item
  \textbf{HTSDiff -- More sensitive differential analysis of RNA-seq
  data}\\
  Statistical analysis of RNA-seq data: Advances and challenges @ Paris
  (2013-11-26)
\item
  \textbf{HTSFilter -- Data-based filtering for replicated
  high-throughput sequencing experiments}\\
  Deuxièmes rencontres R @ Lyon (2013-06-28)
\item
  \textbf{(Invited round table) Statistics applied to RNA-seq}\\
  Journée de la transcriptome végétale de l'URGV-Genopole @ Evry
  (2013-05-16)
\item
  \textbf{Joint estimation of causal effects from observational and
  intervention gene expression data}\\
  StatSeq meeting on genetical genomics @ Paris (2013-03-28)
\item
  \textbf{(Invited talk) A comprehensive evaluation of normalization
  methods for high-throughput RNA sequencing data analysis}\\
  Journée APLIBIO (Alliance des PLates-formes Île-de-France de
  BIOinformatique) @ Paris (2012-10-11)
\item
  \textbf{Clustering high-throughput sequencing data using Poisson
  mixture models}\\
  Joint Statistical Meetings of the American Statistical Association @
  San Diego, California (2012-07-31)
\item
  \textbf{Clustering high-throughput sequencing data using Poisson
  mixture models}\\
  12th Workshop: Statistical Methods for Post-Genomic Data @ Lyon
  (2012-01-26)
\item
  \textbf{Reverse Engineering Gene Networks Using Approximate Bayesian
  Computation}\\
  11th Workshop: Statistical Methods for Post-Genomic Data @ Paris
  (2011-01-27)
\item
  \textbf{Approximate Bayesian methods for reverse engineering
  biological networks}\\
  Conference on Applied Statistics in Agriculture @ Manhattan, Kansas
  (2010-04-26)
\item
  \textbf{Reverse-Engineering Gene Networks from Microarray Data with
  Dynamic Bayesian Networks}\\
  GENESYS Satellite Meeting at the European Conference on Complex
  Systems @ Warwick, UK (2009-09-22)
\item
  \textbf{Using Dynamic Bayesian Networks with Hidden States to Infer
  Gene Regulatory Networks}\\
  Joint Statistical Meetings of the American Statistical Association @
  Washington, DC (2009-08-05)
\item
  \textbf{(Poster) Reverse-Engineering Genetic Regulatory Interactions
  from Transcriptomic Data using Dynamic Bayesian Networks}\\
  2nd Biennial Workshop on Statistical Bioinformatics and Stochastic
  Systems Biology @ Newcastle, UK (2009-05-18)
\item
  \textbf{(Poster) An Empirical Bayes Approach to Inferring Genetic
  Regulatory Interactions with Dynamic Bayesian Networks}\\
  Conference on Applied Statistics in Agriculture @ Manhattan, Kansas
  (2009-04-19)
\item
  \textbf{(Poster) An Empirical Bayes Approach to Inferring Genetic
  Regulatory Interactions with Dynamic Bayesian Networks}\\
  Gordon Conference on Quantitative Genetics and Genomics @ Galveston,
  Texas (2009-02-22)
\item
  \textbf{(Poster) Seven Years of StatCom at Purdue: Managing a Growing
  Number of Student Volunteers}\\
  Joint Statistical Meetings of the American Statistical Association @
  Denver, Colorado (2008-08-04)
\end{enumerate}

\hypertarget{seminar-working-group-presentations}{%
\section{Seminar \& working group
presentations}\label{seminar-working-group-presentations}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Incorporating multiple annotations in genomic prediction
  models}\\
  Integration of gene co-expression networks with genomic prediction
  (IGEN) Workshop, CIRAD @ Montpellier (2022-12-12)
\item
  \textbf{Leveraging multi-omic data for integrative exploratory,
  predictive, and network analyses}\\
  Séminaire Biogeco @ Bordeaux (2022-09-16)
\item
  \textbf{(Poster) Differential network analysis of mixed-type data with
  copulae}\\
  Journées Scientifiques du Département de Génétique Animale @ Bordeaux
  (2022-09-13)
\item
  \textbf{Leveraging multi-omic data for integrative exploratory,
  predictive, and network analyses}\\
  KIM -- Data \& Life Sciences seminar (MUSE) @ Montpellier (2022-05-30)
\item
  \textbf{(Invited talk) A randomized pairwise likelihood method for
  complex statistical inferences}\\
  Séminaire statistique de Paris @ virtual (2022-02-07)
\item
  \textbf{Intégration d'annotations biologiques complexes dans les
  modèles bayésiens de prédiction génomique -- Evaluation et extension
  du modèle BayesRC}\\
  SAPS seminar @ virtual (2022-01-21)
\item
  \textbf{E pluribus unum -- l'intégration de données à GiBBS pour une
  vision unifiée des données hétérogènes complexes}\\
  Lundi de SAPS seminar @ virtual (2021-12-13)
\item
  \textbf{Leveraging multi-omic data for integrative exploratory,
  predictive, and network analyses}\\
  NutriNeurO lab seminar @ virtual (2021-11-22)
\item
  \textbf{Multi-omic integration for enhanced interpretability in
  exploratory analyses}\\
  Grenoble Laboratoire Jean Kuntzmann seminar @ virtual (2021-04-29)
\item
  \textbf{Happy 20th Birthday, R!}\\
  INRAE GiBBS team meeting @ virtual (2020-05-18)
\item
  \textbf{Integrative methods for multi-omic data reveal multi-level
  gene regulation}\\
  AgroParisTech statistics seminar @ Paris, France (2020-01-20)
\item
  \textbf{Integrative multivariate methods for multi-omic data}\\
  Lundi de GABI seminar @ Jouy en Josas, France (2020-01-13)
\item
  \textbf{Integrative methods for multi-omic data reveal multi-level
  gene regulation}\\
  INRA MaIAGE research seminar @ Jouy en Josas, France (2019-11-18)
\item
  \textbf{Integrative methods for multi-omic data reveal multi-level
  gene regulation}\\
  Journée régionale Genotoul @ Toulouse, France (2019-10-04)
\item
  \textbf{Integrative methods for multi-omic data reveal multi-level
  gene regulation}\\
  EpiFun workshop @ Orléans, France (2019-09-17)
\item
  \textbf{Exploring drivers of gene expression in The Cancer Genome
  Atlas}\\
  Division of Biostatistics Seminar at MCW @ Milwaukee, Wisconsin
  (2018-12-04)
\item
  \textbf{Co-expression analyses of RNA-seq data in practice with the
  R/Bioconductor package coseq}\\
  MixStatSeq Workshop on Mixture Models -- Theory and Application @
  Paris (2018-06-22)
\item
  \textbf{Exploring drivers of gene expression in The Cancer Genome
  Atlas}\\
  Research seminar series, Joseph J. Zilber School of Public Health @
  Milwaukee, WI (2018-04-09)
\item
  \textbf{Exploring drivers of gene expression in The Cancer Genome
  Atlas}\\
  Physiology Department Seminar at MCW @ Milwaukee, WI (2018-03-28)
\item
  \textbf{Easy interactivity in R with (gg)plotly and Shiny}\\
  INRA national bioinformatics workshop @ Dijon (2017-06-13)
\item
  \textbf{Challenges in data integration}\\
  SAPS doctoral school -- Experimental animal biology and predictive
  modelisation @ Jouy en Josas, France (2017-03-17)
\item
  \textbf{Transformation, model choice, and visualization for RNA-seq
  co-expression}\\
  Seminar at the Human and Molecular Genetics Center, Milwaukee College
  of Medicine @ Milwaukee, WI (2016-09-10)
\item
  \textbf{Transformation, model choice, and visualization for RNA-seq
  co-expression}\\
  Seminar at the Zilber School of Public Health @ Milwaukee, WI
  (2016-09-09)
\item
  \textbf{Poisson mixtures with slope heuristics and visualization tools
  for RNA-seq co-expression}\\
  Groupe de travail de statistiques du LMRS @ Rouen (2016-05-12)
\item
  \textbf{From genotype to phenotype -- what statistical methods to
  integrate heterogeeous data?}\\
  INRA national bioinformatics workshop @ Toulouse (2016-03-22)
\item
  \textbf{Integration of heterogeneous 'omics data}\\
  SAPS doctoral school: Experimental animal biology and predictive
  modelisation @ Jouy en Josas, France (2016-03-11)
\item
  \textbf{Poisson mixture models and visualization tools for RNA-seq
  co-expression}\\
  INRA NGS club @ Jouy en Josas, France (2016-03-08)
\item
  \textbf{Poisson mixtures with slope heuristics and visualization tools
  for RNA-seq co-expression}\\
  MAP5 seminar at Université Paris-Descartes @ Paris (2016-01-29)
\item
  \textbf{Model selection in mixture model based classification --
  Applications in biostatistics}\\
  4th Annual SFdS Young Statisticians and Probabilists Day @ Paris
  (2016-01-22)
\item
  \textbf{Statistical analysis of microarray and RNA-seq data}\\
  Seminar at Toulouse Mathematics Institute (IMT) @ Toulouse
  (2015-11-17)
\item
  \textbf{Integrative clustering and classification in multiple
  heterogeneous data}\\
  Statomique seminar @ Paris (2015-11-09)
\item
  \textbf{RNA-seq co-expression analysis using mixture models}\\
  NETBIO working group @ Paris (2015-09-29)
\item
  \textbf{HTSCluster, a mixture-based approach for co-expression
  analyses of RNA-seq data}\\
  Cirad seminar @ Montpellier (2015-09-25)
\item
  \textbf{Slope heuristics -- the missing ingredient for identifying
  co-expressed genes from RNA-seq data}\\
  SELECT seminar @ Orsay (2014-10-16)
\item
  \textbf{HTSFilter -- filtering replicated RNA-seq data using a
  data-driven approach}\\
  Statistics for Systems Biology (SSB) seminar @ Evry (2013-11-12)
\item
  \textbf{Reinforcing the biology-statistics feedback loop with tools
  for genomic data analysis}\\
  Seminar at INRA-GABI @ Jouy en Josas, France (2013-11-04)
\item
  \textbf{HTSAnalysis -- a suite of R/Bioconductor packages for the
  analysis of RNA-seq data}\\
  Statistics for Integrative Biology (SIB) seminar @ Rennes (2013-10-29)
\item
  \textbf{Joint estimation of causal effects from observational and
  intervention gene expression data}\\
  NETBIO working group @ Paris (2013-09-20)
\item
  \textbf{Joint estimation of causal effects from observational and
  intervention gene expression data}\\
  Statistique et Santé working group @ Paris (2013-06-24)
\item
  \textbf{Joint estimation of causal effects from observational and
  intervention gene expression data}\\
  AppliBUGS Workshop @ Paris (2013-06-20)
\item
  \textbf{Joint estimation of causal effects from observational and
  intervention gene expression data}\\
  Statistics seminar @ Toulouse (2013-06-18)
\item
  \textbf{Joint estimation of causal effects from observational and
  intervention gene expression data}\\
  Statistics for Integrative Biology seminar @ Rennes (2013-02-22)
\item
  \textbf{Differential analysis of RNA-seq data by unsupervised
  classification}\\
  Assemblée générale PEPI IBIS @ Toulouse (2012-12-07)
\item
  \textbf{Independent data-based filtering for replicated
  high-throughput sequencing experiments}\\
  Statomique seminar @ Lyon (2012-11-27)
\item
  \textbf{Clustering high-throughput sequencing data using Poisson
  mixture models}\\
  LGC and SAGA seminar at INRA @ Toulouse (2012-06-25)
\item
  \textbf{Clustering high-throughput sequencing data using Poisson
  mixture models}\\
  SSB working group seminar @ Jouy en Josas, France (2012-06-19)
\item
  \textbf{Inferring gene regulatory networks with hidden variables using
  state space models}\\
  MIA Biological network inference methodological working group meeting
  @ Paris (2012-02-09)
\item
  \textbf{Exploring the identifiability of gene regulatory networks with
  approximate Bayesian computation}\\
  AppliBugs Workshop @ Paris (2011-12-09)
\item
  \textbf{Reverse Engineering Gene Networks Using Approximate Bayesian
  Computation (ABC)}\\
  Seminar at the Institut de Recherche Mathématique Avancée @ Strasbourg
  (2011-05-24)
\item
  \textbf{Reverse Engineering Gene Networks -- A Statistician's
  Perspective}\\
  Seminar at the Unité de Recherche en Génomique Végétale @ Evry
  (2011-04-07)
\item
  \textbf{Reverse Engineering Gene Networks Using Approximate Bayesian
  Computation (ABC)}\\
  Seminar at the Institut de Mathématiques de Luminy @ Marseille
  (2011-04-04)
\item
  \textbf{Reverse Engineering Gene Networks Using Approximate Bayesian
  Computation (ABC)}\\
  Seminar at the Laboratoire Statistique et Génome @ Evry (2011-03-22)
\item
  \textbf{Reverse Engineering Gene Networks Using Approximate Bayesian
  Computation (ABC)}\\
  Seminar at the équipe Génétique et Génomique Statistique @ Le Kremlin
  Bicêtre (2011-03-02)
\item
  \textbf{Reverse Engineering Gene Networks Using Approximate Bayesian
  Computation (ABC)}\\
  Rencontre de statistique autour des modèles hiérarchiques @ Strasbourg
  (2011-01-14)
\item
  \textbf{Reverse Engineering Gene Networks Using Approximate Bayesian
  Computation (ABC)}\\
  INA P-G, Paris Descartes, and SELECT working group @ Paris
  (2010-10-18)
\item
  \textbf{Approximate Bayesian methods for reverse engineering
  biological networks}\\
  Bioinformatics seminar at Purdue University @ West Lafayette, Indiana
  (2010-04-13)
\item
  \textbf{Inférence sur les réseaux génomiques par des modèles
  espace-état}\\
  Seminar at the AgroParisTech @ Paris (2009-06-22)
\item
  \textbf{Inférence sur les réseaux génomiques par des modèles
  espace-état}\\
  Seminar at the UMR GABI-INRA @ Jouy-en-Josas (2009-06-15)
\item
  \textbf{Reverse Engineering Gene Regulatory Networks}\\
  Ph.D.~student seminar, INRA Département de Génétique Animale @
  Jouy-en-Josas (2009-03-23)
\item
  \textbf{(Poster) Inferring Gene Regulatory Network through Linear
  Feedback State Space Models}\\
  Ph.D.~student seminar, INRA Département de Génétique Animale @
  Toulouse (2008-03-20)
\end{enumerate}

\hypertarget{participation-in-working-groups}{%
\section{Participation in working
groups}\label{participation-in-working-groups}}

\begin{itemize}
\tightlist
\item
  Statomique (2009-present)
\item
  Netbio (2014-present)
\end{itemize}

\hypertarget{software}{%
\section{Software}\label{software}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{BayesRCO}: Bayesian genomic prediction models for overlapping
  annotations, available at
  \href{https://github.com/fmollandin/BayesRCO}{GitHub}\\
\item
  \textbf{rpl}: Randomized pairwise likelihood method for complex
  statistical inferences, available at
  \href{https://github.com/andreamrau/rpl}{GitHub}\\
\item
  \textbf{padma}: Pathway deviation scores using multiple factor
  analysis, available at
  \href{https://bioconductor.org/packages/padma/}{BioC}\\
\item
  \textbf{Invest Astuces}: An R/Shiny interactive web application for
  financial and real estate loan simulations, available as a
  \href{https://investastuces.com/simulateurs/}{Shiny web app}\\
\item
  \textbf{Regeneration Rosetta}: An R/Shiny interactive web application
  to explore regeneration-associated gene expression and chromatin
  accessibility, available as a
  \href{http://ls-shiny-prod.uwm.edu/rosetta/}{Shiny web app}\\
\item
  \textbf{maskmeans}: Multi-view aggregation/splitting K-means
  clustering algorithm, available at
  \href{https://github.com/andreamrau/maskmeans}{GitHub}\\
\item
  \textbf{Edge in TCGA}: An R/Shiny interactive web application for the
  exploration of drivers of gene expression in The Cancer Genome Atlas,
  available as a \href{http://ls-shiny-prod.uwm.edu/edge_in_tcga/}{Shiny
  web app}\\
\item
  \textbf{coseq}: Co-expression analysis of sequencing data, available
  at \href{https://bioconductor.org/packages/coseq/}{BioC}\\
\item
  \textbf{ICAL}: Model selection for model based clustering of annotated
  data, available at \href{https://github.com/Gallopin/ICAL}{GitHub}\\
\item
  \textbf{metaRNASeq}: Meta-analysis of RNA-seq data, available at
  \href{https://cran.r-project.org/web/packages/metaRNASeq/index.html}{CRAN}\\
\item
  \textbf{HTSDiff}: Differential analysis for RNA-seq data, available at
  \href{https://r-forge.r-project.org/R/?group_id=1504}{R-Forge}\\
\item
  \textbf{HTSFilter}: Filter for replicated high-throughput sequencing
  data, available at
  \href{http://www.bioconductor.org/packages/release/bioc/html/HTSFilter.html}{BioC}\\
\item
  \textbf{HTSCluster}: Clustering high-throughput sequencing data with
  Poisson mixture models, available at
  \href{http://cran.r-project.org/web/packages/HTSCluster}{CRAN}\\
\item
  \textbf{ebdbNet}: Empirical Bayes estimation for dynamic Bayesian
  networks, available at
  \href{http://cran.r-project.org/web/packages/ebdbNet}{CRAN}
\end{enumerate}

\hypertarget{administrative-activities}{%
\section{Administrative activities}\label{administrative-activities}}

\begin{cventries}
    \cventry{Annals of Applied Statistics, Bioinformatics, BMC Bioinformatics, BMC Genomics, BMC Medical Genetics, Briefings in Bioinformatics, Computational and Structural Biotechnology Journal, F1000 Research, G3, Genetics Selection Evolution, Genome Biology, GigaScience, IEEE Proceedings, Journal of Computational Biology, Journal of Computational and Graphical Statistics, JRSS-C, Molecular Genetics and Genomics, Nature Computational Science, Nucleic Acids Research, Revue d’Intelligence Artificielle, RNA, Statistical Applications in Genetics and Molecular Biology, The Plant Journal}{Reviewer}{2010-present}{}{}\vspace{-4.0mm}
    \cventry{Evaluation committee for Research Scientist (chargé de recherche) position at INRAE}{Member}{2023}{}{}\vspace{-4.0mm}
    \cventry{Annual INRAE -- WUR-ASG meeting (Wageningen, Netherlands; 21-22 November 2022)}{Delegate}{2022}{}{}\vspace{-4.0mm}
    \cventry{Organization committee, INRAE Data Science Workshop}{Member}{2022}{}{}\vspace{-4.0mm}
    \cventry{INRAE GABI Conseil d'unité}{Elected member}{2022-2024}{}{}\vspace{-4.0mm}
    \cventry{Institut Agro Rennes-Angers internal PhD funding call}{Reviewer}{2022}{}{}\vspace{-4.0mm}
    \cventry{Evaluation committee for Research Scientist (chargé de recherche) position at INRAE}{Member}{2022}{}{}\vspace{-4.0mm}
    \cventry{INRAE Animal Genetics Department Conseil Scientifique}{Elected member (substitute)}{2021-2024}{}{}\vspace{-4.0mm}
    \cventry{INRAE Commission scientifique spécialisée (CSS) Mathématiques, Informatique, Sciences et Technologies du numérique, Intelligence artificielle et Robotique (MISTI}{Appointed member}{2021-2024}{}{}\vspace{-4.0mm}
    \cventry{INRAE GABI Scientific Communication and Mediation committee}{Member}{2021-present}{}{}\vspace{-4.0mm}
    \cventry{Saclay Plant Sciences Research Open Call}{Reviewer}{2021}{}{}\vspace{-4.0mm}
    \cventry{Evaluation committee for Assistant Professor position at Université Le Mans}{Member}{2021}{}{}\vspace{-4.0mm}
    \cventry{Evaluation committee for Research Scientist (chargé de recherche) position at INRAE}{Member}{2021}{}{}\vspace{-4.0mm}
    \cventry{ANR MRSEI grant call}{Reviewer}{2020}{}{}\vspace{-4.0mm}
    \cventry{UseR!2019 international conference}{Scientific committee member}{2019}{}{}\vspace{-4.0mm}
    \cventry{University of Wisconsin-Milwaukee Research Growth Initiative grant call}{Reviewer}{2017}{}{}\vspace{-4.0mm}
    \cventry{INRA Selgen Metaprogramme grant call}{Reviewer}{2017}{}{}\vspace{-4.0mm}
    \cventry{Nantes Excellence Trajectory (NExT) Health and Engineering initiative "Internal interdisciplinary project" call}{Reviewer}{2017}{}{}\vspace{-4.0mm}
    \cventry{Evaluation committee for Assistant Professor position at Université Rennes I, UMR Inserm IRSET 1085}{Member}{2016}{}{}\vspace{-4.0mm}
    \cventry{Evaluation committee for Assistant Professor position at Université Rennes I, IGDR (Institute of Genetics and Developmental biology of Rennes), CNRS UMR 6290}{Member}{2016}{}{}\vspace{-4.0mm}
    \cventry{Rencontres R national conference}{Scientific committee president}{2016}{}{}\vspace{-4.0mm}
    \cventry{Conseil Scientifique des Utilisateurs (CSU) of the MIGALE Bioinformatics platform (INRA, Jouy en Josas)}{Member}{2015-2019}{}{}\vspace{-4.0mm}
    \cventry{Committee on Student Pro Bono Statistics of the ASA}{Chair}{2010}{}{}\vspace{-4.0mm}
    \cventry{Committee on Student Pro Bono Statistics of the American Statistical Association (ASA)}{Member}{2009-2010}{}{}\vspace{-4.0mm}
    \cventry{Invited round table (The Pros of Pro Bono Statistics) at the ASA Joint Statistical Meetings (Washington, DC, USA}{Organizer}{2009}{}{}\vspace{-4.0mm}
    \cventry{Statistics in the Community (StatCom) at Purdue University: StatCom is a volunteer organization of graduate students that provides free professional statistical consulting services to government and nonprofit groups}{Member}{2006-2010}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{funding}{%
\section{Funding}\label{funding}}

\begin{cventries}
    \cventry{Animal holobionts: a new biological scale to explore genetic diversity and refine breeding strategies for agroecology, French National Research Agency (ANR) PEPR Agroécologie et Numérique}{HOLOBIONTS}{2022-2027}{}{\begin{cvitems}
\item PI: Jordi Estellé and Sylvie Combes; Role: Partner
\end{cvitems}}
    \cventry{Genomic and functional characterizon of domestic plant and animal genetic diversity as sa keystone for agroecology: linking genome to phenome, French National Research Agency (ANR) PEPR Agroécologie et Numérique}{AgroDiv}{2022-2027}{}{\begin{cvitems}
\item PI: Jérome Salse, Gwendal Restoux, Matthias Zytnicki, Pierre Peterlongo, and François Parcy; Role: WP co-leader
\end{cvitems}}
    \cventry{Pénétrance incomplète et expressivité variable : études des mécanismes dans un cas de palais fendu, INRAE Animal Genetics Department internal grant}{Pixel}{2022}{}{\begin{cvitems}
\item PI: Amandine Duchesne; Role: Partner
\end{cvitems}}
    \cventry{Genome and Epigenome eNabled breddIng in MOnogastrics, EU H2020 RIA grant}{GEroNIMO}{2021-2025}{}{\begin{cvitems}
\item PI: Frédérique Pitel and Tatiana Zerjal; Role: Partner
\end{cvitems}}
    \cventry{Automatic recording and analysis of lactating sow postural activity, France Futur Elevage (F2E) grant}{WHAT-SOW}{2021-2024}{}{\begin{cvitems}
\item PI: Laurianne Canario; Role: Partner
\end{cvitems}}
    \cventry{Differential network analysis of mixed-type data with copulae, INRAE DIGIT-BIO metaprogram grant}{DINAMIC}{2021-2023}{}{\begin{cvitems}
\item PI: Andrea Rau
\end{cvitems}}
    \cventry{The regulatory genome of swine and chicken: functional annotation during development, EU H2020 RIA grant}{GENE-SWitCH}{2019-2023}{}{\begin{cvitems}
\item PI: Elisabetta Giuffra and Herve Acloque; Role: Task leader
\end{cvitems}}
    \cventry{Characterisation of a minipig spontaneous regression model with no invalidating adverse effects, Inserm Plan cancer 2014-2019, New Experimental Models call}{MiniSRegress}{2019-2021}{}{\begin{cvitems}
\item PI: Giorgia Egidy-Maskos; Role: Partner
\end{cvitems}}
    \cventry{Towards a better understanding of ruminant milk lipolysis through an integrative biology approach in milk and mammary epithelial cells, French National Research Agency (ANR) grant}{LIPOMEC}{2018-2022}{}{\begin{cvitems}
\item PI: Christelle Cebo; Role: WP leader
\end{cvitems}}
    \cventry{Systems biology for genomic selection, INRA Selgen metaprogram grant}{EpiFun}{2018-2020}{}{\begin{cvitems}
\item PI: Nathalie Vialaneix and Thomas Faraut; Role: Partner
\end{cvitems}}
    \cventry{Integrative analysis of multi-omics data for improved detection power of functional genetic variants, AgreenSkills+ mobility grant (University of Wisconsin-Milwaukee)}{AgreenSkills+}{2017-2019}{}{\begin{cvitems}
\item PI: Andrea Rau
\end{cvitems}}
    \cventry{Relationships between digestive microbiota and feed efficiency in cattle, AP-2016-007}{Microficient}{2016-2019}{}{\begin{cvitems}
\item PI: Yuliaxis Ramayo and Gilles Renand; Role: Partner
\end{cvitems}}
    \cventry{Characterization and management of health and environmental risks linked to the development of ciguatera in phytobenthos in French Polynesia, French Polynesia Territory grant}{CARISTO-PF}{2016-2019}{}{\begin{cvitems}
\item PI: Gregory Nuel; Role: Partner
\end{cvitems}}
    \cventry{Genetic and microbiotal control of Salmonella carriage in chicken and mice, Institut Carnot Pasteur Maladies Infectieuses (PMI) / Institut Carnot Santé Animale (ICSA) grant}{SalmoCar}{2015-2017}{}{\begin{cvitems}
\item PI: Xavier Montagutelli; Role: Partner
\end{cvitems}}
    \cventry{Using COmbinatorial gene Silencing \& Inactivation to infer gene NETworks, INRA Animal Genetics Department internal grant}{COSI-net}{2015-2016}{}{\begin{cvitems}
\item PI: Andrea Rau
\end{cvitems}}
    \cventry{Mixture-based procedures for statistical analysis of RNA-seq data, French National Research Agency (ANR) grant (ANR-13-JS01-0001-01)}{MixStatSeq}{2014-2018}{}{\begin{cvitems}
\item PI: Cathy Maugis-Rabusseau; Role: WP leader
\end{cvitems}}
    \cventry{Causal network inference, INRA Animal Genetics Department internal grant}{Causality}{2014}{}{\begin{cvitems}
\item PI: Florence Jaffrézic; Role: Partner
\end{cvitems}}
\end{cventries}

\hypertarget{advising}{%
\section{Advising}\label{advising}}

\begin{cventries}
    \cventry{PhD}{Fanny Mollandin}{2019-2022}{}{\begin{cvitems}
\item Incorporating known functional annotations into Bayesian genomic prediction models (with Pascal Croiseau, co-funding from EU Horizon 2020 RIA grant GENE-SWitCH)
\end{cvitems}}
    \cventry{M2 internship}{See Hyun Park}{2022}{}{\begin{cvitems}
\item Impact of nutritional supplement intervention on cognitive health networks (with Jean-Christophe Delpech and Charlotte Madore-Delpech)
\end{cvitems}}
    \cventry{Postdoc}{Smahane Chalabi}{2021-2022}{}{\begin{cvitems}
\item A diet x epigenetics study in pigs, GENE-SWitCH grant (with Elisabetta Giuffra and Sarah Djebali)
\end{cvitems}}
    \cventry{6-month CDD}{Maxime Guilleton}{2021}{}{\begin{cvitems}
\item Bioinformatics research engineer, LIPOMEC grant (with Mylène Delosiere)
\end{cvitems}}
    \cventry{L2 internship}{Alexandre Asset}{2021}{}{\begin{cvitems}
\item Inference of co-expression networks from intervention transcriptomic data (with Florence Jaffrézic and Denis Laloë)
\end{cvitems}}
    \cventry{M1 internship}{Solène Pety}{2021}{}{\begin{cvitems}
\item Knowledge transfer using multivariate gene expression projections onto a large-scale reference database (with Catherine Giauffret)
\end{cvitems}}
    \cventry{M2 internship}{Raphaëlle Momal-Leisenring}{2017}{}{\begin{cvitems}
\item Integrative statistical analysis of multi-omics data
\end{cvitems}}
    \cventry{M2 internship}{Frédéric Jehl}{2017}{}{\begin{cvitems}
\item Impact of heat stress on liver and blood transcriptomes of laying hens (with Tatiana Zerjal)
\end{cvitems}}
    \cventry{3-month PhD Erasmus+ Learning Mobility}{Manuel Revilla Sanchez}{2016}{}{\begin{cvitems}
\item An integrative gene network analysis of the genetic determination of pig fatty acid composition (with Jordi Estelle and Yuliaxis Ramayo Caldas)
\end{cvitems}}
    \cventry{M2 internship}{Babacar Ciss}{2016}{}{\begin{cvitems}
\item Constructing predictive models for ovine production data (with Eli Sellem)
\end{cvitems}}
    \cventry{M1 internship}{Audrey Hulot}{2015}{}{\begin{cvitems}
\item Incorporating a priori biological knowledge into gene network inference from observational and intervention gene expression data (with Florence Jaffrézic)
\end{cvitems}}
    \cventry{M1 internship}{Meriem Benabbas}{2015}{}{\begin{cvitems}
\item Identifying differentially expressed genes from RNA-seq data using mixture models
\end{cvitems}}
    \cventry{PhD}{Gilles Monneret}{2014-2018}{}{\begin{cvitems}
\item Estimation of causal effects in gene networks from observational and intervention data (with Grégory Nuel and Florence Jaffrézic)
\end{cvitems}}
    \cventry{M1 STV/EM-ABG internship}{Marc Teissier and Chaoyu Dong}{2014}{}{\begin{cvitems}
\item Power to detect significantly differential gene expression using RNA-seq data
\end{cvitems}}
    \cventry{PhD}{Mélina Gallopin}{2012-2015}{}{\begin{cvitems}
\item Clustering and network inference for RNA-seq data (with Gilles Celeux and Florence Jaffrézic)
\end{cvitems}}
    \cventry{M2 internship}{Rémi Bancal}{2012}{}{\begin{cvitems}
\item Gene network estimation by adaptive knockout experiments (with Grégory Nuel and Florence Jaffrézic)
\end{cvitems}}
    \cventry{M2 internship}{Mélina Gallopin}{2012}{}{\begin{cvitems}
\item Gene network inference from RNA sequencing expression data (with Gilles Celeux and Florence Jaffrézic)
\end{cvitems}}
\end{cventries}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{cventries}
    \cventry{HDR evaluation committee member (rapportrice)}{Bénédicte Wenden}{2023}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member (examinatrice)}{Ousmane Suwareh}{2022}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member}{Fotini Panagou}{2022}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member (rapportrice)}{Océane Cassan}{2022}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member (evaluatrice)}{Camille Kergal}{2022}{}{}\vspace{-4.0mm}
    \cventry{PhD advisory committee member}{Baber Ali}{2021-2024}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member (rapportrice)}{Ambre Giguelay}{2021}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member (rapportrice)}{Leila Khajavi}{2021}{}{}\vspace{-4.0mm}
    \cventry{PhD advisory committee member}{Thibault Poinsignon}{2021-2023}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member (rapportrice)}{Nicolas Jouvin}{2021}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member (rapportrice)}{Lucile Broséus}{2021}{}{}\vspace{-4.0mm}
    \cventry{PhD advisory committee member}{Wilfried Heyse}{2020-2022}{}{}\vspace{-4.0mm}
    \cventry{PhD advisory committee member}{Antoine Leduc}{2019-2022}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member (rapportrice)}{Alyssa Imbert}{2018}{}{}\vspace{-4.0mm}
    \cventry{PhD advisory committee member}{Frédéric Jehl}{2017-2020}{}{}\vspace{-4.0mm}
    \cventry{PhD evaluation committee member}{Valentin Voillet}{2016}{}{}\vspace{-4.0mm}
    \cventry{PhD advisory committee member}{Gabriel Guillocheau}{2015-2018}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\begin{cventries}
    \cventry{Instructor @ Lyon}{Atelier IA: Mes clusters ont-ils un sens ? Quelques indices de la statistique et de la biologie… (1670457600)}{2022}{}{\begin{cvitems}
\item Séminaire métaprogramme DIGIT-BIO
\end{cvitems}}
    \cventry{Instructor @ Orsay}{UE Bioinfo, Master Bioinformatique et Biostatistiques Paris-Saclay (November-December)}{2022}{}{\begin{cvitems}
\item Co-expression, genomic prediction, and multi-omic analyses
\end{cvitems}}
    \cventry{Instructor (with M.-L. Martin-Magniette and E. Delannoy) @ INRAE, BioEcoAgro}{Researcher training session: From gene expression to genomic networks (1-2 March)}{2022}{}{\begin{cvitems}
\item Co-expression and network analysis of RNA-seq data
\end{cvitems}}
    \cventry{Instructor (with S. Lagarrigue and Y. Blum) @ Rennes}{Agrocampus Researcher School (23 June)}{2021}{}{\begin{cvitems}
\item Statistical analysis of RNA-seq data
\end{cvitems}}
    \cventry{Instructor (with S. Lagarrigue and Y. Blum) @ Rennes}{Agrocampus Researcher School (6-7 February)}{2020}{}{\begin{cvitems}
\item Statistical analysis of RNA-seq data
\end{cvitems}}
    \cventry{Instructor (with M.-L. Martin-Magniette and E. Delannoy) @ INRAE, BioEcoAgro}{Researcher training session: From gene expression to genomic networks (2-3 December)}{2019}{}{\begin{cvitems}
\item Differential analysis of RNA-seq data
\end{cvitems}}
    \cventry{Instructor (with J. Estellé @ INRA URZ, Guadeloupe}{Analysis of livestock metagenomics datasets (13-17 May)}{2019}{}{}\vspace{-4.0mm}
    \cventry{Instructor @ Medical College of Wisconsin}{Physiological genomics (10 hours)}{2019}{}{\begin{cvitems}
\item R Bootcamp
\end{cvitems}}
    \cventry{Instructor @ University of Wisconsin-Milwaukee}{Data management and visualization in R (3 course units)}{2018}{}{}\vspace{-4.0mm}
    \cventry{Instructor @ INRA, Jouy en Josas}{PiGutNet Training School (3 hours)}{2017}{}{\begin{cvitems}
\item Differential abundance analysis for microbial marker-gene surveys with metagenomeSeq
\end{cvitems}}
    \cventry{Instructor (coursework and labs) @ Université d'Evry Val d'Essonne}{Bayesian statistics for genomics course (18 hours)}{2017}{}{\begin{cvitems}
\item Mathematics for the Life Sciences: Statistical Engineering and Genomics, M2
\end{cvitems}}
    \cventry{Instructor (with S. Lagarrigue and Y. Blum) @ Rennes}{Agrocampus Researcher School (1-2 February)}{2017}{}{\begin{cvitems}
\item Statistical analysis of RNA-seq data
\end{cvitems}}
    \cventry{Instructor (coursework and labs) @ Ensai, Rennes}{Genomics course (12 hours)}{2017}{}{\begin{cvitems}
\item Biostatistics M2
\end{cvitems}}
    \cventry{Instructor (coursework and labs) @ Institute of Plant Sciences Paris-Saclay}{SPS Summer School: From gene expression to genomic networks (17-22 July)}{2016}{}{\begin{cvitems}
\item Co-expression analysis of RNA-seq data (3 hours
\end{cvitems}}
    \cventry{Instructor (coursework and labs) @ Université d'Evry Val d'Essonne}{Bayesian statistics for genomics course (18 hours)}{2016}{}{\begin{cvitems}
\item Mathematics for the Life Sciences: Statistical Engineering and Genomics, M2
\end{cvitems}}
    \cventry{Instructor (with S. Lagarrigue and Y. Blum) @ Rennes}{Agrocampus Researcher School (10-11 February)}{2016}{}{\begin{cvitems}
\item Statistical analysis of RNA-seq data
\end{cvitems}}
    \cventry{Instructor (coursework and labs) @ Ensai, Rennes}{Genomics course (33 hours)}{2016}{}{\begin{cvitems}
\item Biostatistics M2
\end{cvitems}}
    \cventry{Instructor (coursework and labs) @ Université Paris Descartes}{Mathematical Engineering for Life Sciences Master, M1: Case study (10 hours)}{2015}{}{}\vspace{-4.0mm}
    \cventry{Instructor (coursework and labs) @ Ensai, Rennes}{Genomics course (33 hours)}{2015}{}{\begin{cvitems}
\item Biostatistics M2. Note: The genomics course at Ensai was significantly expanded and re-developed in 2015 by myself and Mickaël Guedj.
\end{cvitems}}
    \cventry{Scientific committee member and instructor (coursework and labs) @ Cannes Mandelieu}{BioBayes Researcher School (7-11 October)}{2013}{}{\begin{cvitems}
\item Bayesian statistical methods: Introduction to theory and applications in food, environment, epidemiology, and genetics
\end{cvitems}}
    \cventry{Instructor (coursework and labs) @ Ensai, Rennes}{Genomics course (6 hours)}{2013}{}{\begin{cvitems}
\item Biostatistics M2
\end{cvitems}}
    \cventry{Instructor @ COST action research school, Norwich, United Kingdom}{Training school on rabbit and pig genome analysis (6 hours)}{2012}{}{}\vspace{-4.0mm}
    \cventry{Instructor (coursework and labs) @ Ensai, Rennes}{Genomics course (6 hours)}{2012}{}{\begin{cvitems}
\item Biostatistics M2
\end{cvitems}}
    \cventry{Instructor @ European Graduate School in Animal Breeding and Genetics, Paris}{Statistical Methods for Genome Enabled Prediction (2 hours)}{2012}{}{\begin{cvitems}
\item Approximate Bayesian methods: Application to gene regulatory networks
\end{cvitems}}
    \cventry{Instructor @ INRA research school, Ecully}{Next generation sequencing school for INRA researchers (2 hours)}{2012}{}{}\vspace{-4.0mm}
    \cventry{Instructor (coursework and labs) @ UFR de Sciences, Université Paris-Sud 11}{Computational biostatistics (6 hours)}{2012}{}{\begin{cvitems}
\item Bioinformatics and Biostatistics / Mathematical engineering / Probability and Statistics M2
\end{cvitems}}
    \cventry{Lab assistant (R) @ UFR de Sciences, Université Paris-Sud 11}{Statistical modeling (24 hours)}{2011}{}{\begin{cvitems}
\item Bioinformatics and Biostatistics Master, M1
\end{cvitems}}
    \cventry{Instructor (coursework and labs) @ UFR de Sciences, Université Paris-Sud 11}{Bioinformatics and Biostatistics / Mathematical engineering / Probability and Statistics M2 (12 hours)}{2011}{}{\begin{cvitems}
\item Bioinformatics and Biostatistics / Mathematical engineering / Probability and Statistics M2
\end{cvitems}}
    \cventry{Lab assistant (SPSS) @ Department of Statistics, Purdue University (West Lafayette, Indiana, USA)}{Elementary statistical methods (60 hours)}{2006}{}{\begin{cvitems}
\item 1st and 2nd year undergraduate
\end{cvitems}}
\end{cventries}

\hypertarget{outreach}{%
\section{Outreach}\label{outreach}}

\begin{cventries}
    \cventry{Steering committee, Université Paris-Saclay Women and Science Mentoring Program}{Member}{2023-present}{}{}\vspace{-4.0mm}
    \cventry{Elementary school activity for the Fête de la Science: "La meilleure recette pour comprendre les données... la science des données!"}{Organizer}{2022}{}{}\vspace{-4.0mm}
    \cventry{Video about Bayesian models and simulations for H2020 GENE-SWitCH project: https://youtu.be/VWEBe2Wpi60}{Creator}{2022}{}{}\vspace{-4.0mm}
    \cventry{Celebrating Women in Statistics and Data Science featured profile for the American Statistical Association: https://magazine.amstat.org/blog/2022/03/01/andrea-rau}{Author}{2022}{}{}\vspace{-4.0mm}
    \cventry{Video about Data Science for H2020 GENE-SWitCH project: https://twitter.com/i/status/1501490287931179012}{Creator}{2022}{}{}\vspace{-4.0mm}
    \cventry{GEroNIMO Hackathon: A 360° perspective on new genomic solutions for addressing the challenges in sustainable livestock production}{Facilitator}{2022}{}{}\vspace{-4.0mm}
    \cventry{Université Paris-Saclay Women and Science Mentoring Program}{Mentor}{2021-2023}{}{}\vspace{-4.0mm}
    \cventry{Elementary school (CE2/CM1/CP2) classroom activity for the Fête de la Science: "Data science: from data to discovery!"}{Organizer}{2021}{}{}\vspace{-4.0mm}
\end{cventries}

\end{document}
