---
name: Andrea
surname: Rau
position: "Research Scientist &bull; Chargée de Recherche"
address: "INRAE &bull; French National Research Institute for Agriculture, Food and Environment"
phone: +33 1 34 65 22 82
www: andrea-rau.com
email: "andrea.rau@inrae.fr"
twitter: andreamrau
github: andreamrau
orcid: 0000-0001-6469-488X
googlescholar: 9__bzfgAAAAJ
date: "January 2022"
output:
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(vitae)
library(tibble)
library(glue)
library(googlesheets4)
library(dplyr)
id <- "1szi9SA4sKl9Fmh-MWrepS1M9T36-HLvMSpyW9RJh-ws"
# gs4_deauth()
# gs4_auth()
```

<!-- date: "`r format(Sys.time(), '%B %Y')`" -->


# About me

My research is focused on developing and writing software for sound statistical methods for genomic and transcriptomic data analysis, including differential expression analyses, co-expression analyses, network inference, and integrative multi-omic analyses. 

I currently belong to two INRAE labs:  

- [**Animal Genetics and Integrative Biology**](https://www6.jouy.inra.fr/gabi_eng/) (GABI) research unit (Jouy en Josas, France) in the Genomics, Biodiversity, Bioinformatics, Statistics (GiBBS) team  
- Cross-border [**BioEcoAgro**](https://www.bioecoagro.eu/) research unit (Estrées-Mons, France)

*Keywords*: Analysis of high-throughput sequencing data, mixture models, supervised classification methods, multi-omic integration, gene regulatory networks

*Languages*: English (maternal), French (fluent)

# Education

```{r, cache=TRUE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="education")
d %>% 
  detailed_entries(institution, location, degree, year, title,
                   .protect=FALSE)
# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
#   "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
#   "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
# ) %>% 
#   detailed_entries(Degree, Year, Institution, Where)
# tribble(
#   ~Year, ~Type, ~Desc,
#   1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
#   1911, "Chemistry", "Awarded for the discovery of radium and polonium"
# ) %>% 
#   brief_entries(
#     Desc,
#     Type,
#     # glue::glue("Nobel Prize in {Type}"),
#     Year
#   )
```

# Work experience

```{r, cache=TRUE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="positions")
d %>% 
  detailed_entries(institution, location, title, year, 
                   .protect=FALSE)
```

# Awards

```{r, cache=TRUE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="awards")
d %>% mutate(arrow = "\\rightarrow") %>%
  brief_entries(with=year, what=description, when = arrow,
                   .protect=FALSE)
```

# Professional organizations

```{r}
tribble(~year, ~name, ~shortname,
        "2022-present", "Femmes & Sciences", "F&S",
        "2011-present", "Société Française de la Statistique", "SFdS",
        "2005-present", "American Statistical Association", "ASA") %>%
  brief_entries(with=year, when=shortname, what=name)
```

# Dissertations, books & book chapters

```{r, cache=TRUE, results="asis"}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="publications")
tmp <- d %>% filter(type %in% c("dissertation", "book", "book chapter")) %>%
  arrange(desc(year)) %>%
  select(year, title, authors, journal, details, doi) %>%
  mutate(authors_bf = sub(authors, pattern="Rau, A.", 
                          replacement="**Rau, A.**"),
         journal_it = paste0("*",journal,"*")) %>%
  mutate(details_full = ifelse(is.na(details), ".", paste0(", ", details))) %>%
  mutate(full = 
           glue("1. {authors_bf} ({year}) {title}. {journal_it}, {details}.")) %>%
  select(full) %>%
  unclass()
tmp$full
```

# Peer-reviewed publications

```{r, cache=TRUE, results="asis"}
#options(encoding = "UTF-8")
#knitr::write_bib(c("vitae", "tibble"), "packages.bib")
# bibliography_entries("packages.bib") %>%
#   arrange(desc(author$family), issued)

d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="publications")
tmp <- d %>% filter(type %in% c("article")) %>%
  arrange(desc(year)) %>%
  select(year, title, authors, journal, details, doi) %>%
  mutate(authors_bf = sub(authors, pattern="Rau, A.", 
                          replacement="**Rau, A.**"),
         journal_it = paste0("*",journal,"*")) %>%
  mutate(details_full = ifelse(is.na(details), ".", paste0(", ", details))) %>%
  mutate(doi_full = ifelse(is.na(doi), ".", paste0(". ", "https://dx.doi.org/",doi))) %>%
  mutate(full = 
    glue("1. {authors_bf} ({year}) {title}. {journal_it}{details_full}{doi_full}")) %>%
  select(full) %>%
  unclass()
tmp$full
```


# Pre-prints, technical reports, & other publications

```{r, cache=TRUE, results="asis"}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="publications")
tmp <- d %>% filter(type %in% 
                      c("other", "submitted", "techreport", "conference")) %>%
  arrange(desc(year)) %>%
  select(year, title, authors, journal, details, url_preprint) %>%
  mutate(authors_bf = sub(authors, pattern="Rau, A.", 
                          replacement="**Rau, A.**"),
         journal_it = ifelse(is.na(journal), ".", paste0(". *",journal,"*"))) %>%
  mutate(details_full = ifelse(is.na(details), ".", paste0(" ", details))) %>%
  mutate(url_preprint_full = ifelse(is.na(url_preprint), ".", 
                                    paste0(". ", url_preprint))) %>%
  mutate(full = 
    glue("1. {authors_bf} ({year}) {title}{journal_it}{details_full}{url_preprint_full}")) %>%
  select(full) %>%
  unclass()
tmp$full
```

# Conference presentations

```{r, cache=TRUE, results="asis"}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="talks")
tmp <- d %>% filter(type == "conference") %>%
  arrange(desc(date)) %>%
  select(date, title, event, location) %>%
  mutate(full = glue("1. **{title}**  
                     {event} @ {location} ({date})")) %>%
  select(full) %>%
  unclass()
tmp$full
```

# Seminar & working group presentations

```{r, cache=TRUE, results="asis"}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="talks")
tmp <- d %>% filter(type == "seminar") %>%
  arrange(desc(date)) %>%
  select(date, title, event, location) %>%
  mutate(full = glue("1. **{title}**  
                     {event} @ {location} ({date})")) %>%
  select(full) %>%
  unclass()
tmp$full
```

# Participation in working groups

- Statomique (2009-present)
- Netbio (2014-present)

# Software

```{r, cache=TRUE, results="asis"}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="software")
tmp <- d %>% mutate(full1 = glue("1. **{title}**: {description}, available at [{repo}]({url_software})  "),
                    full2 = glue("1. **{title}**: {description}, available as a [{repo}]({url_software})  ")) %>%
  mutate(full = ifelse(repo == "Shiny web app", full2, full1)) %>%
  mutate(full = as_glue(full)) %>%
  select(full) %>%
  unclass()
tmp$full
```


# Administrative activities

```{r, cache=TRUE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="administrative")
d %>%
  detailed_entries(with=role, what=description, where=year,
                   .protect=FALSE)
```

# Funding

```{r, cache=FALSE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="funding")
d %>%
  mutate(description = 
           glue("{full_name}, {agency}"),
         role_full = ifelse(PI == "Andrea Rau", 
                            glue("PI: {PI}"),
                            glue("PI: {PI}; Role: {role}"))) %>%
  detailed_entries(with=acronym, what=description, where=year,
                   why=role_full,
                   .protect=FALSE)
```

# Advising


```{r, cache=TRUE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="advising")
tmp <- d %>% mutate(arrow = "\\rightarrow") %>%
  mutate(desc = glue("{name} ({type})")) %>%
  mutate(desc2 = ifelse(!is.na(cosupervision), 
                        glue("{title} (with {cosupervision})"), 
                        glue("{title}")))
tmp %>% filter(desc2 != "NA") %>%
   detailed_entries(with=name, where=year, why=desc2, what=type,
                   .protect=FALSE)
```

---

```{r, cache=TRUE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="advising")
tmp <- d %>% mutate(arrow = "\\rightarrow") %>%
  mutate(desc = glue("{name} ({type})")) %>%
  mutate(desc2 = ifelse(!is.na(cosupervision), 
                        glue("{title} (with {cosupervision})"), 
                        glue("{title}")))

tmp %>% filter(desc2 == "NA") %>%
   detailed_entries(with=name, where=year, what=type,
                   .protect=FALSE)
```

# Teaching


```{r, cache=TRUE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="teaching")
d %>% 
  mutate(name_full = glue("{name} ({dates})")) %>%
  mutate(desc =  glue("{type} @ {location}")) %>%
  detailed_entries(where=year, with=name_full, 
                   why=description, what=desc,
                   .protect=FALSE)
```

# Outreach

```{r, cache=TRUE}
d <- googlesheets4::range_read(googlesheets4::as_sheets_id(id),
                               sheet="outreach")
d %>%
  detailed_entries(with=role, what=description, where=year,
                   .protect=FALSE)
```
